### 2021-12-15 README.Rmd

The goal of `taxadb` is to provide *fast*, *consistent* access to taxonomic data, supporting common tasks such as resolving taxonomic names to identifiers, looking up higher classification ranks of given species, or returning a list of all species below a given rank. These tasks are particularly common when synthesizing data across large species assemblies, such as combining occurrence records with trait records.

@@

>>>>

The goal of `taxadb` is to provide *fast*, *consistent* access to taxonomic data, supporting common tasks such as resolving taxonomic names to identifiers, looking up higher classification ranks of given species, or returning a list of all species below a given rank. These tasks are particularly common when synthesizing data across large species assemblies, such as combining occurrence records with trait records (see `taxadb` companion paper [Norman et al. 2020](https://doi.org/10.1111/2041-210X.13440)).

@@

## How to cite `taxadb`?

You can access the citation information through `citation("taxadb")` within R, which refers to `taxadb` companion paper:

> Kari E. A. Norman, Scott Chamberlain, and Carl Boettiger (2020). taxadb: A high-performance local taxonomic
>  database interface. Methods in Ecology and Evolution, 11(9), 1153-1159.
>  https://besjournals.onlinelibrary.wiley.com/doi/abs/10.1111/2041-210X.13440.
